---
title: 'SNP Dataset Analysis'
author: "Sara Tagol"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
csl: bioinformatics.csl
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      error = FALSE)
```

## Setup

```{r setup-chunk}
# Path to the SNP file
snp_file <- "data/sample_snp_data.csv"

# Sample ID for subsetting
sample_id <- "SRR12433063"
```

```{r load-packages}
library(dplyr)
library(ggplot2)
source("code/functions/single_function.R")
```

## Project Description
This project analyzes a SNP dataset to identify the SNPs associated with a specific sample. The Sample SNP data set has information about the SNPs including chromosome, position number, and the samples they were taken from. The goal of this project is to subset the data and to the sample with the ID `SRR12433063`.


```{r subset-data}
# Pass only the snp_file and sample_id arguments
single_sample_data <- subset_snp_data(snp_file = snp_file,
                                      sample_id = sample_id)

# Create a csv file for the subsetted data 
output_file <- paste0("data/subset_snp_data_", sample_id, ".csv")
write.csv(single_sample_data, file = output_file, row.names = FALSE)

# Confirmation message
cat("Subset file saved as:", output_file)
```

## Figures
### Scatterplot of SNP Quality Scores by Position
The scatter plot was created using the `ggplot2` package [@ggplot22016].


```{r snp-scatterplot, echo=FALSE, message=FALSE, warning=FALSE}
# Make the scatter plot 
scatter_plot <- ggplot(single_sample_data, aes(x = pos, y = qual)) +
  geom_point(alpha = 0.6) +
  labs(
    title = paste("SNP Quality Scores by Position for Sample", sample_id),
    x = "Position in Genome",
    y = "SNP Quality Score"
  ) +
  theme_minimal()

# Display the plot
print(scatter_plot)

# Save the plot to a file
ggsave(filename = paste0("output/scatterplot_snp_quality_", sample_id, ".png"), plot = scatter_plot, width = 8, height = 6)
```

## Session Info
This report was generated using the `rmarkdown` package [@rmarkdown2021] and `knitr` [@knitr2021].

```{r session-info, echo=FALSE}
# Display session information
devtools::session_info()
```

## Sources Cited
